### 2022-09-04 Papers/ICCC-2023/sections/implementation.tex
implementation

Languages that seek to exploit CTFE First approach in design of their compilers, should define a set of data structures to describe user code, i.e. an Semantic Model.
It will allow the programmer to interact and mainpulate the structure of the program at compile-time.

@@

\subsection{Program semantic model}

@@

The most complex part of the model is the representation of the function body.

>>>>

Languages that seek to exploit CTFE First approach in design of their compilers, should define a set of data structures to describe user code, i.e. an Semantic Model.
It will allow the programmer to interact and mainpulate the structure of the program at compile-time.
The Semantic model designed and implemented for C-=-1 is described in chapter \ref{semantic_model}.

The final piece of a CTFE First compiler is the Backend Interface.
It is a program, written in the target language, and ran at compile-time that translates the semantic model into the backends assembly language.
Backend Interface implemented for C-=-1 is relativley small and has been described in chapter \ref{implementation/backend-interface}.

@@

\subsection{Program semantic model}
\label{semantic_model}

@@

The most complex part of the model is the representation of the function body.
Like in most programming languages, a C-=-1 function can contain a variety of instruction types.
That includes complex statements and blocks of statements that can be arbitrarly nested.
Each instruction may also contain expressions of any complexity.

To deal with this complexity, C-=-1 semantic model for functions is build around two interfaces: \lstinline{IInstruction} and \lstinline{IExpression} and their concrete implementations.
